Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-07 jss/article.tex
[skip ci] jss update

The statistical significance of the counts in the modules is assessed by using
either the Fisher exact test \citep{fisher1922interpretation,
fisher1934statistical} or the hypergeometric test, which are equivalent for this
purpose \cite{rivals2007enrichment}.

@@

>>>>

The statistical significance of the counts in the modules is assessed by using
either the Fisher exact test \citep{fisher1922interpretation,
fisher1934statistical} or the hypergeometric test, which are equivalent for this
purpose \citep{rivals2007enrichment}.

@@

Once the RNaviCell library is installed and loaded, the first step is to create
a NaviCell object and launch the browser session. This will automatically create
a unique session ID with the NaviCell server. Once the session is established,
various functions can be called to send data to the web session, set graphical
options, visualize data on a map or get data from the map. There are 125
functions available in the current version of RNaviCell. All of them are
described with their different options in the RNaviCell documentation, and we
provide a tutorial on the GitHub repository wiki
(\url{https://github.com/sysbio-curie/RNaviCell/wiki/Tutorial}).
